\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-05-02 project-writings/paper.tex
oops

These results show that our range analysis is generally quite
successful in eliminating overflow checks from programs, but our
timing results indicate that this does yield that substantial of a
performance improvement. We believe that this is because the overhead
of an essentially never taken branch on modern hardware are quite
low. While on a microbenchmark we constructed overflow check
elimination resulted in a substantial (!30\%) speedup, it appears that
this does not translate well to more realistic code.

>>>>

These results show that our range analysis is generally quite
successful in eliminating overflow checks from programs, but our
timing results indicate that this does yield that substantial of a
performance improvement. We believe that this is because the overhead
of an essentially never taken branch on modern hardware are quite
low. While on a microbenchmark we constructed overflow check
elimination resulted in a substantial (around 30\%) speedup, it appears that
this does not translate well to more realistic code.
